%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software/Machine Learning Engineer} % Job title
    {\href{https://www.jungle.ai}{Jungle AI}} % Organization
    {Lisbon, Portugal} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched and implemented Jungle’s core approach to predictive modelling with a emphasis on recurrent models and time series data implementing from scratch most of the modules using Pytorch.}
        \item {Active member of 5+ projects within the energy and heavy industry sector with the main purpose of showing Jungle’s predictive solutions. This work would evolve to gather, process and analyze data to apply Jungle's predictive maintenance pipeline and presenting the result to the clients.}
        \item {Designed, developed and build internal and production-ready software and deployments. Tasks like ORM definition for production databases, software to process essential high-volume data analysis or the development of a backend infrastructure to manage production deployments using FastAPI, among others.}
        \item {Designed and implemented a database architecture (Postgres and TimescaleDB) refactor to allow for a scalable, high-performing and cost-effective solution.}
        \item {Built an automated data collection and cleaning workflow (AWS S3 and Prefect) to process daily 2k+ sensors with a millisecond frequency.}
        \item {Built a CRUD RESTful API in Node.js for TimescaleDB and PostgresSQL database to be used by Jungle product.}
        \item {Implemented, deployed and maintained several high-performing, scalable and distributed workflows using Argo and Kubernetes to different business needs.}
        \item {Designed, built and managed an internal dashboards and data warehouse solution using InfluxDB and Grafana to allow for high-volume data analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master Thesis Internship} % Job title
    {\href{https://www.jungle.ai}{Jungle AI}} % Organization
    {Lisbon, Portugal} % Location
    {August 2018 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Had the opportunity to do my master thesis work in a professional environment. The main research goal was to study, implement and test the performance of different deep learning models and architectures applied to time-series problems, specifically on the area of predictive maintenance and forecasting. This allowed me to be an active member of Jungle’s daily projects to establish their technology.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
